Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-12-17 2016-Weak-FH-Bisim/WeakBisim.tex
2 todos et delimitation de l exemple

\subsection{Bisimulation for open pNets -- a Composable Bisimulation Theory}
\label{section:bisimulation-PN}
As  our symbolic operational semantics provides an open automaton, we can apply the notion of
	strong (symbolic) bisimulation on automata to open pNets:
\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation (with some initial predicate).
\TODO{check}
\end{definition}
%\TODO{Predicate=True me pose un probleme... typiquement, on a besoin d'une ``condition initiale'', pour avoir des pNets data-oriented equivalents a leur version state-oriebted => remove the constraint}

@@

\begin{example}
  Figures \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA. We show on the top one possible sequence corresponding to a weak transition, on the bottom left the concerned subset of the original OA, and on the right the generated weak transition.
\end{example}

@@

\begin{definition}[Notation: Semantics of pNets as a weak open automaton]
Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automata derived from $A$. For any $\WOT\in\WT$, we denote $\pNet \models \WOT$, this defines the semantics of the pNet $\pNet$ as a weak open automaton. \TODO{strange sentence}
\end{definition}

>>>>

\subsection{Bisimulation for open pNets -- a Composable Bisimulation Theory}
\label{section:bisimulation-PN}
As  our symbolic operational semantics provides an open automaton, we can apply the notion of
	strong (symbolic) bisimulation on automata to open pNets:
\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation (i.e. the predicate associated with the initial states is verifiable).
%\TODO{check}
\end{definition}
%\TODO{Predicate=True me pose un probleme... typiquement, on a besoin d'une ``condition initiale'', pour avoir des pNets data-oriented equivalents a leur version state-oriebted => remove the constraint}

@@

\begin{example}
  Figures \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA. We show on the top one possible sequence corresponding to a weak transition, on the bottom left the concerned subset of the original OA, and on the right the generated weak transition.

@@

\begin{definition}[Notation: Semantics of pNets as a weak open automaton]
Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$. Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.
\end{definition}
